\begin{thebibliography}{9}
\bibitem{ciferki}
Don’t Let Your Sensitive Information Leak onto Social Networks: Information Leakage with Zecurion Zgate
\bibitem{IDS}
W. Zhengi, W. Xinyu NetFlow Based Intrusion Detection System
\bibitem{Analys}
G. Munz, G. Carle Real-time Analysis of Flow Data for Network Attack Detection
\bibitem{Work1}
F. Benevenuto, T. Rodrigues, M. Cha, and V. Almeida. Characterizing user navigation and interactions in on-line social networks. Inf. Sci., July 2012.
\bibitem{Work2}
N. V. Verde, G. Ateniese, E.Gabrielli, L. V. Mancini. No nat’d user left behind: Fingerprinting users behind NAT from netflow records alone, 2014

\bibitem{methodologies1} 
Hofstede, Rick; Celeda, Pavel; Trammell, Brian; Drago, Idilio; Sadre, Ramin; Sperotto, Anna; Pras, Aiko. Flow Monitoring Explained: From Packet Capture to Data Analysis with NetFlow and IPFIX". IEEE Communications Surveys Tutorials. IEEE Communications Society.
\bibitem{instagram1} 
http://www.businessinsider.com/instagram-2010-11
\bibitem{facebookStats}
https://www.statista.com/statistics/272014/global-social-networks-ranked-by-number-of-users/ - Statistic about amount of users in social networks
\bibitem{Selenium}
http://www.seleniumhq.org/ - main page of Selenium browser automation project
\bibitem{Phantomjs}
http://phantomjs.org/ - main page of headless WebKit
\bibitem{fbDevelop}
https://developers.facebook.com/docs/sharing/webmasters/crawler - information about Facebook for developers
\bibitem{nfdump}
https://pythonhosted.org/pynfdump/ - official site of package pynfdump
\end{thebibliography}
